\pdfbookmark[1]{Abstract}{Abstract}
\begingroup

\chapter*{Abstract}

\noindent\spacedlowsmallcaps{Keywords}: Web Application, Layered Architecture, REST API Modelling, Trending Topics, News, Responsive Design.
\begin{center}
· · ·
\end{center}

The main focus of this Final Degree Project is based on providing useful information, summarized and easily accessible to the end user, without it being overwhelming and difficult to read.

\vspace{0.3cm}

To this day, the most dominant social web applications on the market try to engage and keep the user as long as possible. They achieve this by providing a huge or almost infinite amount of information. This information is updated everytime, giving the possibility of staying involved in the social world almost forever.

\vspace{0.3cm}

Given the overwhelming abundance of information, I have decided to make a web application that provides you with information in a much simpler way about current trends. In this sense, users will not have to be so focused on keeping up to date, but at the end of the day they will have summarized the most valuable information and useful data based on the trend.

\vspace{0.3cm}

The idea that this project tries to carry out is the management of trends from the Twitter API and the extraction of relevant content based on the trend, such as the volume of publications, keywords, general sentiments or relevant news.

\vspace{0.3cm}

The project involves all the knowledge, both in computer engineering and outside of it, that I have been able to acquire throughout my learning cycle in the computer field. In addition to studying the programmable and functional part of the application, a rigorous study is carried out on the most ideal planning, structure and architecture to the project.

\vspace{0.3cm}

Going into more detail in the applied knowledge, the project will be approached with a layered architecture and an API REST model. The mostly used programming languages will be JavaScript, Python and the type of databases will be NoSQL.

\vspace{0.3cm}

However, throughout the project the reason for these decisions will be studied and it will be demonstrated how by combining these technologies, a single application is achieved for the end user.

\vfill
